Data Management for LSST Special Programs

### 2023-05-20 sec_intro.tex
Update sec_intro.tex

Special Programs includes non-WFD LSST components such as the Deep Drilling 
Fields (DDFs) and the mini-, micro-, and nano-surveys; some of these components
might use non-standard visits with different exposure times
(see Section~\ref{ssec:intro_terms}, below, for details).

@@

\textbf{Wide-Fast-Deep (WFD) Main Survey -- }
The core science program of the LSST, designed to achieve the science 
goals defined by the Science Requirements Document (SRD; \citeds{LPM-17}).

It is a contiguous area that covers at least $\sim$18000 deg$^2$ with 
$\gtrsim$800 visits per field, expected to be accomplished with 85--90\% 
of the observing time.
As of the Phase 2 SCOC recommendations in \citeds{PSTN-055}, the WFD area 
is considered to include the low dust extinction extragalactic regions; 
the higher extinction, high stellar density Galactic Plane and Bulge; the 
Virgo Cluster; the South Celestial Pole (SCP); and the North Ecliptic Spur 
(NES).

In the past, the Galactic, SCP, and NES regions have been referred to as 
"mini-surveys", and the scheduler software might treat them as such, but 
this does not make them "Special Programs". 
From a survey-scheduling perspective, they are now considered part of the 
WFD survey.
From a science and data-processing perspective, these components of the 
WFD do not require special processing or separate data products.

@@

From a science and data-processing perspective, the DDFs do require 
special processing or separate data products.

\textbf{Mini-, Micro- and Nano-Surveys -- }
Specific sky areas covered by a few hundred, a hundred, or tens of visits 
(respectively; as in Phase 2 SCOC recommendations, \citeds{PSTN-055}).
For a list of the current mini-surveys under consideration, see 
\citeds{PSTN-055}.

This document refers to them all together as mini-surveys.

@@

The Phase 2 SCOC recommendations for the WFD (\citeds{PSTN-055}) are to 
use alternative standard visits in the $u$-band and standard visits in all 
other bands; variable exposure times were not recommended for the WFD.

Non-standard visits with shorter or longer exposure times are being 
considered for some mini-surveys.

>>>>

Special Programs includes non-WFD LSST components such as the Deep Drilling 
Fields (DDFs) and the mini-, micro-, and nano-surveys, some of which 
might use non-standard visits with different exposure times
(Section~\ref{ssec:intro_terms}).

@@

\textbf{Wide-Fast-Deep (WFD) Main Survey -- }
The core science program of the LSST, designed to achieve the science 
goals defined by the Science Requirements Document (SRD; \citeds{LPM-17}).
It is a contiguous area that covers at least $\sim$18000 deg$^2$ with 
$\gtrsim$800 visits per field, expected to be accomplished with 85--90\% 
of the observing time.

As of the Phase 2 SCOC recommendations in \citeds{PSTN-055}, the WFD area 
is considered to include the low dust extinction extragalactic regions; 
the higher extinction, high stellar density Galactic Plane (GP) and Bulge; the 
Virgo Cluster; the South Celestial Pole (SCP); and the North Ecliptic Spur 
(NES).

In the past the Galactic, SCP, and NES regions have been referred to as 
``mini-surveys" (see below) but this does not make them "Special Programs". 
From a survey-scheduling perspective, they are now considered part of the 
WFD survey (whether or not the scheduler software treats them as such).

From a science and data-processing perspective, these components of the 
WFD do not require special processing or separate data products 
(i.e., do not need to be treated by RDM as ``Special Programs").
This is because they will use standard (or alternative) visits and can
be incorporated into WFD Prompt processing (Section~\ref{ssec:proc_wfd}), 
and because their distinct areas do not overlap with the other WFD components 
and so do not require, e.g., separate deep coadds.

@@

From a science and data-processing perspective, the DDFs do require 
special processing and separate data products (Section~\ref{ssec:proc_rdm}).

\textbf{Mini-, Micro- and Nano-Surveys -- }
Specific sky areas covered by a few hundred, a hundred, or tens of visits 
(respectively; as in Phase 2 SCOC recommendations, \citeds{PSTN-055}).
For a list of the current mini-surveys under consideration, see 
\citeds{PSTN-055}.
This document refers to them all together as mini-surveys.

@@

The Phase 2 SCOC recommendations for the WFD (\citeds{PSTN-055}) are to 
use alternative standard visits in the $u$-band and standard visits in all 
other bands; variable exposure times were not recommended for the WFD. 
Non-standard visits with shorter or longer exposure times are being 
considered for some mini-surveys.
